Discrete Quantum Theories and Computing

### 2019-02-05 dissertation.tex
dissertation.lyx ACKNOWLEDGMENTS Updates, and commit before adjust the spacing in document class...

me, suggested me as a committee member, and taught me, and the collaboration

@@

\begin{sidewaystable}
\noindent \begin{centering}
\caption{\label{tab:teacher}The knowledge I learned from teachers in other
courses help me consolidate this dissertation, where IUB stands for
Indiana University Bloomington and NTU stands for National Taiwan
University.}
\par\end{centering}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{ccM{MATH-M522}M{English~for~International~Graduate~Students:}Y}
\toprule 
\addlinespace
Instructor & School & Course & Title & Relation with the dissertation\tabularnewline\addlinespace
\midrule
\addlinespace
\midrule 
\addlinespace
Tom Lewis & IUB & SLST-T501 & English for International Graduate Students:\linebreak[3] Academic
Writing & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Michael A. Mandell & IUB & MATH-M522 & Topology II & The textbook~\cite{Hatcher2001} is cited in Chapters~\ref{chap:Introduction}
and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Valery Lunts & IUB & MATH-M501 & Survey of Algebra & The textbook~\cite{DummitFoote2004} is cited in Sec.~\ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\addlinespace
\midrule 
\addlinespace
Huah Chu (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & Algebra(I)\linebreak[3] Algebra(II) & The textbook~\cite{Artin1991} is cited in Sec.~\ref{CQC1qubitBloch.sec},
\ref{sec:background}, \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\midrule
\addlinespace
\addlinespace
Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
\bottomrule
\addlinespace
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{sidewaystable}
To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Besides of my committee members,
the knowledge I learned from teachers in other courses help me consolidate
this dissertation as listed in Table~\ref{tab:teacher}.

Besides of Prof.\ Tom Lewis, my other English teachers, especially
Traci Nagle, Elizabeth ``Betsy'' Merceron, and Kexin ``Casey''
Chen (谌可心), taught me a lot on how to communicate in English as well.
Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
could be listed on and on. I still thank you even if your name is
not listed here, and sorry for my bad memory.

Many people in both the departments of Mathematics and Computer Science
have done everything to make my double-major smooth. \todo{Acknowledgments
cleaned up until here. }I need to thank all of them, especially directors
of graduate study in Mathematics, especially Prof.\ Christopher Judge
and Prof.\ Matthias Weber; directors of Ph.D. study in Computer Science,
especially Prof.\ Yuqing Melanie Wu (吴愈青) and Prof.\ \textturkish{Funda
Ergun}.

>>>>

me, suggested me as a committee member, and taught me; the collaboration

@@

\begin{sidewaystable}
\noindent \begin{centering}
\caption{\label{tab:teacher}The knowledge I learned from teachers in other
courses help me consolidate this dissertation, where IUB stands for
Indiana University Bloomington and NTU stands for National Taiwan
University.}
\par\end{centering}
%% ERT block 1 (before LyX tabular)
\renewcommand{\tabular}{\tabularx{\linewidth}}
\renewcommand{\endtabular}{\endtabularx} 
\begin{tabular}{ccM{MATH-M522}M{English~for~International~Graduate~Students:}Y}
\toprule 
\addlinespace
Instructor & School & Course & Title & Relation with the dissertation\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
Tom Lewis & IUB & SLST-T501 & English for International Graduate Students:\linebreak[3] Academic
Writing & Sec.~\ref{subsec:Discrete-Deutsch-algorithm} is based on the term
paper.\tabularnewline\addlinespace
\midrule 
\addlinespace
Michael A. Mandell & IUB & MATH-M522 & Topology II & The textbook~\cite{Hatcher2001} is cited in Chapters~\ref{chap:Introduction}
and~\ref{chap:Conventional-Quantum-Theory}.\tabularnewline\addlinespace
\midrule 
\addlinespace
Steven Myers & IUB & CSCI-B502 & Computational Complexity & The textbook~\cite{AroraBarak2009} is cited in Sec.~\ref{modalquantumcomputing}.\tabularnewline\addlinespace
\midrule 
\addlinespace
Valery Lunts & IUB & MATH-M501 & Survey of Algebra & The textbook~\cite{DummitFoote2004} is cited in Sec.~\ref{sec:background},
\ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\midrule 
\addlinespace
Huah Chu (朱樺\textenglish[variant=american]{)} & NTU & 221~U3830\linebreak[3] 221~U3840 & Algebra(I)\linebreak[3] Algebra(II) & The textbook~\cite{Artin1991} is cited in Sec.~\ref{CQC1qubitBloch.sec},
\ref{sec:background}, \ref{discretequantumtheoryI}, and~\ref{sec:Discrete-Quantum-Theory-(II)}.\tabularnewline\addlinespace
\midrule
\addlinespace
Jin-Tzu Chen (陳金次) & NTU & 201~31300 & Functions of a Complex Variable & The textbook~\cite{GAMELIN2003} is cited in Sec.~\ref{subsec:Vector-Spaces}.\tabularnewline\addlinespace
\bottomrule
\end{tabular}% ERT block 2 (after LyX tabular)
\renewcommand{\tabular}{\ORIGtabular}
\renewcommand{\endtabular}{\ORIGendtabular} 
\end{sidewaystable}
To have the current the content of the dissertation, I would also
like to thank John Gardiner for some inspiring discussion about quantum
probability measures over finite fields~\cite{Gardiner2014}. His
results were improved and motivated the transition from DQT to QIVPM
in Sec.~\ref{sec:Toward-IVPM}. Besides of my committee members,
the knowledge I learned from teachers in other courses help me consolidate
this dissertation as listed in Table~\ref{tab:teacher}. Although
not directly relating to the dissertation, I have to thank for your
teaching to make me more mature and easier to communicate with others,
especially my English teachers, Traci Nagle, Elizabeth ``Betsy''
Merceron, and Kexin ``Casey'' Chen (谌可心).

Many people in both the departments of Mathematics and Computer Science
have done everything to make my double-major smooth. \todo{Acknowledgments
cleaned up until here. }I need to thank all of them, especially directors
of graduate study in Mathematics, especially Prof.\ Christopher Judge,
Prof.\ Matthias Weber, and Prof.\ Michael A.\ Mandell; directors
of Ph.D. study in Computer Science, especially Prof.\ Yuqing Melanie
Wu (吴愈青) and Prof.\ \textturkish{Funda Ergun}.

Others who help me indirectly on the content of the dissertation including
Kin Wai Chan, Weihua Liu (刘伟华), Caren Liu (劉鈺平), Meng-Wei Chen
(陳孟瑋), Hao-Chun Lee (李浩君), Chao-Hong Chen (陳昭宏)\ldots , etc. This
could be listed on and on. I still thank you even if your name is
not listed here, and sorry for my bad memory.
